---
title: "Thesis_analysis"
author: "Cande Torres"
date: "2/20/2022"
output: 
    prettydoc::html_pretty:
    theme: cayman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(tidyr)
library(readr)
library(ggplot2)
library(dplyr)
library(broom)
library(readxl)
library(janitor)
library(lubridate)
library(stringr)
library(haven)
library(ggthemes)
library(prettydoc) # Options code_folding, code_download and toc_float are not applicable.
library(reshape2)
library(car)
```

```{r}
ICT_sch <- read_csv("ICT_data_sch_4.csv", 
    col_types = cols(...1 = col_skip(), ICT_index = col_number(), 
        avg_ICT_index = col_number()))
```

```{r}
schooling_controls <- read_csv("wrangle_data_1.0.csv", 
    col_types = cols(...1 = col_skip()))
```

# Rename values to match them 

```{r}
schooling_controls<-schooling_controls %>% 
mutate(country = str_replace(country, "North Macedonia", "Macedonia"))
```

```{r}
schooling_controls<-schooling_controls %>% 
  mutate(country = str_replace(country, "Russian Federation", "Russia"))
```

```{r}
schooling_controls<-schooling_controls %>% 
 mutate(country = str_replace(country, "Republic of Korea", "Korea"))
```

```{r}
schooling_controls<-schooling_controls %>% 
  mutate(country = str_replace(country, "Hong Kong SAR, China", "Hong Kong"))
```


```{r}
schooling_controls<-schooling_controls %>% 
  mutate(country = str_replace(country, "United States", "United States"))
```
```{r}
ICT_sch<-ICT_sch%>% 
  mutate(country = str_replace(country, "United States", "United States"))
```


# Join Data (fourth time)

```{r}
fourth_join<-left_join(ICT_sch, schooling_controls, by="country") #this data set is super large because it contains all the schools per country but we are only using the average of all schools 
```

__COVID-19__

```{r}
df1<-fourth_join %>% 
  group_by(avg_deaths, avg_cases, country) %>% 
  summarise() %>% 
  select(unique.x=country)
```

__Rename__

```{r}
df1 <-df1 %>% 
  transmute(country=unique.x)
```

```{r}
names(df1)[names(df1) == "avg_cases"] <- "Average cases"
names(df1)[names(df1) == "avg_deaths"] <- "Average deaths"
```

```{r}
df2 <- df1 %>% 
  arrange(desc(`Average cases`)) %>% 
  head(10) %>% 
  melt(id.vars='country')
df2<-df2 %>% mutate(value_decimal = value/100000)
df2<-df2 %>% mutate(label= round(value_decimal, digits= 2))
#df2<-df2 %>% mutate(label= round(value_decimal, digits = -3))

```

```{r}
df2 %>% 
  ggplot(aes(x=fct_reorder(country, value_decimal, max), y=value_decimal, fill=variable))+
  geom_bar(stat='identity', position='dodge')+
  theme_minimal()+
  labs( x="Countries",
        title="Top-10 Countries with higher confirmed COVID-19 cases",
        caption="Graph by Cande Torres")+
  scale_y_continuous(name="COVID-19 Impact (per hundred thousand)", breaks=seq(0,55,5))+
  geom_text(aes(label = label),
            position= position_dodge(width=0.9), 
            vjust=-0.5,
            hjust=0.6
            )+
  theme_economist()+
  theme(axis.title.x = element_text(margin = margin(t = 20)),
        axis.title.y = element_text(margin = margin(r = 20)),
        axis.text.y = element_text(size=rel(0.7)))+
  scale_fill_brewer(palette = "Set1")+
  guides(x=guide_axis(angle = 25))+
  expand_limits(y = 55)
```

# Create full IV

```{r}
names(fourth_join)
```
```{r}
fourth_join<-fourth_join %>% 
  filter(!is.na(ceoworld_index)) %>% mutate(edu_r=instruction_rank+ceoworld_index)
```

```{r}
fourth_join<-fourth_join%>% 
  filter(!is.na(ceoworld_index)) %>% mutate(edu_s=schooling_time_index+ceoworld_index)
```

```{r}
fourth_join$avg_nCFR<- as.numeric(fourth_join$avg_nCFR)
fourth_join$avg_adjCFR<- as.numeric(fourth_join$avg_adjCFR)
```

# Running Summary statistics 

__ICT index__  
Main Independent Variable.

```{r}
summary(fourth_join$avg_ICT_index)
sd(fourth_join$avg_ICT_index)
```
__Education: Schooling + Quality__  
Dependent Variable. 
```{r}
summary(fourth_join$edu_s)
sd(fourth_join$edu_s)
```

```{r}
library(vtable)
```
```{r}
df4<-fourth_join %>% 
  group_by(CNT, avg_ICT_index, edu_s, schooling_time_index, gdp_per_capita,literacy_rate,h_sys_inf_index, avg_cases, avg_deaths, avg_stringency, avg_gresponse, avg_containtment,avg_econsupport,avg_nCFR,avg_adjCFR,avg_hp_index, country) %>% 
  summarise() %>% 
  select(unique.x=country)
```
```{r}
df4 <-df4 %>% 
  transmute(country=unique.x)
```
```{r}
df4$avg_nCFR<- as.numeric(df4$avg_nCFR)
df4$avg_adjCFR<- as.numeric(df4$avg_adjCFR)
```



__Summary Stats Table__
```{r}
st(df4)
```


sumstat <- states %>%

    # Select and rename five variables 
    select(
        `Black (%)` = blkpct,
        `Attend church (%)` = attend_pct,
        `Supported Bush in 2000 (%)` = bush00,
        `Supported Obama in 2008 (%)` = obama08,
        `Women in State Legislature (%)` = womleg
        ) %>%

    # Find the mean, st. dev., min, and max for each variable 
    summarise_each(funs(mean, sd, min, max)) %>%

    # Move summary stats to columns
    gather(key, value, everything()) %>% 
    separate(key, into = c("variable", "stat"), sep = "_") %>%
    spread(stat, value) %>%

    # Set order of summary statistics 
    select(variable, mean, sd, min, max) %>%

    # Round all numeric variables to one decimal point
    mutate_each(funs(round(., 1)), -variable)

sumstat


```{r}
sumstats<- df4 %>% 
  #select and rename 
  group_by(CNT) %>% 
  select(
    `ICT index`= avg_ICT_index,
    `Educational Resilience`= edu_s,
    `Log GDP per capita` = gdp_per_capita,
    `Literacy Rate`= literacy_rate,
    `Strengh of health system index` = h_sys_inf_index,
    `COVID-19 cases`= avg_cases,
    `COVID-19 deaths`= avg_deaths,
    `Stringency index`=avg_stringency,
    `Government Response`= avg_gresponse,
    `Containtment of the virus`= avg_containtment,
    `Economic Support`= avg_econsupport,
    `Critical Fatality Ratio (squared)`= sq_nCFR
  ) %>% 
# Find the mean, st. dev., min, and max for each variable 
    summarise_each(funs(n, mean, sd, min, max)) %>%
 # Move summary stats to columns
    gather(key, value, everything()) %>% 
    separate(key, into = c("variable", "stat"), sep = "_") %>%
    spread(stat, value) %>%
 # Set order of summary statistics 
    select(variable, n, mean, sd, min, max) %>%
 # Round all numeric variables to one decimal point
    mutate_each(funs(round(., 1)), -variable)
```

```{r}
labs <- data.frame(
    `ICT index`= avg_ICT_index,
    `Educational Resilience`= edu_s,
    `Log GDP per capita` = gdp_per_capita,
    `Literacy Rate`= literacy_rate,
    `Strengh of health system index` = h_sys_inf_index,
    `COVID-19 cases`= avg_cases,
    `COVID-19 deaths`= avg_deaths,
    `Stringency index`=avg_stringency,
    `Government Response`= avg_gresponse,
    `Containtment of the virus`= avg_containtment,
    `Economic Support`= avg_econsupport,
    `Critical Fatality Ratio (squared)`= sq_nCFR
    )
st(sumstats)
```

```{r}
write.table(tab, file = "tab.txt", sep = ",", quote = FALSE, row.names = F)
```


```{r}
df6<- df4 %>%  
  
  #select and rename 
  select(
    `ICT index`= avg_ICT_index,
    `Educational Resilience`= edu_s,
    `Log GDP per capita` = log_gdp,
    `Literacy Rate`= literacy_rate,
    `Strengh of health system index` = h_sys_inf_index,
    `COVID-19 cases`= avg_cases,
    `COVID-19 deaths`= avg_deaths,
    `Stringency index`=avg_stringency,
    `Government Response`= avg_gresponse,
    `Containtment of the virus`= avg_containtment,
    `Economic Support`= avg_econsupport,
    `Health Policy Index (2020)`= avg_hp_index,
    `Critical Fatality Ratio (squared)`= sq_nCFR
  ) 
df6<-df6 %>% 
  group_by(CNT) %>% 
  select(-schooling_time_index, -avg_nCFR, -avg_adjCFR, -gdp_per_capita)
```

```{r}
st(df6)
```



```{r}
write.txt(tab, file = "tab.csv", sep = ",", row.names = F)
```

```{r}
library(kableExtra)
library(psych)
tab<-describe(df6 [, c("ICT index",
    "Educational Resilience",
    "Log GDP per capita",
    "Literacy Rate",
    "Strengh of health system index",
    "COVID-19 cases",
    "COVID-19 deaths",
    "Stringency index",
    "Government Response",
    "Containtment of the virus",
    "Economic Support",
    "Health Policy Index (2020)",
    "Critical Fatality Ratio (squared)" ) ], fast=TRUE)
print(tab, digits = 3, signif = 3)

kbl(tab) %>% 
  kable_classic(full_width = FALSE, html_font = "Cambria", font_size=16)
```

```{r}
library (pastecs)
summary_df <- stat.desc(df6) 
```

#Trying to export to LATEX

```{r}
library(stargazer)

stargazer(df6)
```

```{r}
library(xtable)
#library(longtable)
print(xtable(tab, type = "latex", tabular.environment="longtable"), file = "test.tex", include.rownames=TRUE)
```

```{r}
t<-df6 %>% 
group_by(CNT) %>% 
summary(~.)
```


```{r}
df6 %>% 
group_by(CNT) %>% 
summary()
```

```{r}
stargazer(tab)
```


## Histograms 

```{r}
df4 %>% 
  group_by(country) %>% 
  ggplot(aes(x= avg_ICT_index))+
  geom_histogram(#binwidth = 0.5, 
                 fill="navy blue")+
  labs(title="Distribution of ICT index levels achieved by countries",
       x= "ICT availability",
       caption = "Graph by Cande Torres")+
  theme_economist()+
  theme(axis.title.x = element_text(margin = margin(t = 20)),
        axis.title.y = element_text(margin = margin(r = 20)),
        axis.text.y = element_text(size=rel(0.7)))
```

```{r}
fourth_join %>% 
  group_by(country) %>% 
  ggplot(aes(x= ICT_index))+
  geom_histogram(binwidth = 0.5, fill="navy blue")+
  labs(title="Distribution of ICT index levels achieved by schools",
       x= "ICT availability",
       caption = "Graph by Cande Torres")+
  theme_economist()+
  theme(axis.title.x = element_text(margin = margin(t = 20)),
        axis.title.y = element_text(margin = margin(r = 20)),
        axis.text.y = element_text(size=rel(0.7)))
```


```{r fig.width= 8}
df4 %>% 
  group_by(country) %>% 
  ggplot(aes(x= edu_s))+
  geom_histogram(binwidth = 20, fill="navy blue")+
  labs(title="Distribution of Education resilince levels achieved by countries in 2020",
       x= "Education Resiliance",
       caption = "Graph by Cande Torres")+
  theme_economist()+
  theme(axis.title.x = element_text(margin = margin(t = 20)),
        axis.title.y = element_text(margin = margin(r = 20)),
        axis.text.y = element_text(size=rel(0.7)))
```

- Normal distribution for both (kinda).  

```{r fig.width=6}
fourth_join %>% 
  select(gdp_per_capita, literacy_rate, h_sys_inf_index) %>% 
  pivot_longer(cols = everything(),
               names_to = "variable",
               values_to = "value") %>% 
  ggplot(aes(x=value))+
  geom_histogram(bins = 30, fill="navy blue")+
  facet_wrap(vars(variable),
             scales = "free")+
  theme_economist()+
  guides(x=guide_axis(n.dodge = 2))+
  labs(x=" ")
```

- GDP per capita is left skewed. Literacy rate is right skewed.  I will log them.

__Transforming GDP__

```{r}
fourth_join$log_gdp <- log(fourth_join$gdp_per_capita + 0.00000000000000001)
df4$log_gdp <- log(df4$gdp_per_capita + 0.00000000000000001)
```

```{r fig.width=6}
fourth_join %>% 
  select(log_gdp, literacy_rate, h_sys_inf_index) %>% 
  pivot_longer(cols = everything(),
               names_to = "variable",
               values_to = "value") %>% 
  ggplot(aes(x=value))+
  geom_histogram(bins = 30, fill="navy blue")+
  facet_wrap(vars(variable),
             scales = "free")+
  theme_economist()+
  guides(x=guide_axis(n.dodge = 2))+
  labs(x=" ")
```

```{r}
fourth_join %>% 
  group_by(country) %>% 
  ggplot(aes(x= literacy_rate))+
  geom_histogram(#binwidth = 0.5, 
    fill="navy blue")+
  labs(title="Literacy Rate Distribution",
       x= " ",
       caption = "Graph by Cande Torres")+
  theme_economist()+
  theme(axis.title = element_text(margin = margin(t = 20)),
        axis.title.y = element_text(margin = margin(r = 20)),
        axis.text.y = element_text(size=rel(0.7)))
```

- Although the distribution is skewed, log transforming it would not be the solution because it would give me the percentages (Literacy rate is already a percentage). 

- Checking the distribution of other controls. 

```{r}
df4 %>% 
  group_by(country) %>% 
  ggplot(aes(x= avg_nCFR))+
  geom_histogram( 
    fill="navy blue")+
  labs(title="CFR Distribution",
       x= " ",
       caption = "Graph by Cande Torres")+
  theme_economist()+
  theme(axis.title = element_text(margin = margin(t = 20)),
        axis.title.y = element_text(margin = margin(r = 20)),
        axis.text.y = element_text(size=rel(0.7)))
```
__Adjusted CFR__

```{r}
df4 %>% 
  group_by(country) %>% 
  ggplot(aes(x= avg_adjCFR))+
  geom_histogram( 
    fill="navy blue")+
  labs(title="CFR Distribution",
       x= " ",
       caption = "Graph by Cande Torres")+
  theme_economist()+
  theme(axis.title = element_text(margin = margin(t = 20)),
        axis.title.y = element_text(margin = margin(r = 20)),
        axis.text.y = element_text(size=rel(0.7)))
```
Both are supper skewed and need logs

```{r}
#Ask Amy about this, in class she said something about the log transforms with this 0.0000..1, something along the lines of "Don't do it". 
fourth_join$log_nCFR<-log(fourth_join$avg_nCFR+ 0.00000000000000001)
fourth_join$log_aCFR<-log(fourth_join$avg_adjCFR+ 0.00000000000000001)
df4$log_nCFR<-log(df4$avg_nCFR + 0.00000000000000001)
df4$log_aCFR<-log(df4$avg_adjCFR + 0.00000000000000001)
```
```{r}
#Logging wont work because duh they are already rates 

fourth_join$sq_nCFR<-(fourth_join$avg_nCFR)^2
fourth_join$sq_aCFR<-(fourth_join$avg_adjCFR)^2
df4$sq_nCFR<-log(df4$avg_nCFR)^2
df4$sq_aCFR<-log(df4$avg_adjCFR)^2
```

__RE-DO GRAPHS__

```{r}
df4 %>% 
  group_by(country) %>% 
  ggplot(aes(x= log_nCFR))+
  geom_histogram( 
    fill="navy blue")+
  labs(title="CFR Distribution",
       x= " ",
       caption = "Graph by Cande Torres")+
  theme_economist()+
  theme(axis.title = element_text(margin = margin(t = 20)),
        axis.title.y = element_text(margin = margin(r = 20)),
        axis.text.y = element_text(size=rel(0.7)))
```


```{r}
df4 %>% 
  group_by(country) %>% 
  ggplot(aes(x= log_aCFR))+
  geom_histogram( 
    fill="navy blue")+
  labs(title="CFR Distribution",
       x= " ",
       caption = "Graph by Cande Torres")+
  theme_economist()+
  theme(axis.title = element_text(margin = margin(t = 20)),
        axis.title.y = element_text(margin = margin(r = 20)),
        axis.text.y = element_text(size=rel(0.7)))
```
FIXED!

```{r}
df4 %>% 
  group_by(country) %>% 
  ggplot(aes(x= avg_hp_index))+
  geom_histogram( 
    fill="navy blue")+
  labs(title="HP index",
       x= " ",
       caption = "Graph by Cande Torres")+
  theme_economist()+
  theme(axis.title = element_text(margin = margin(t = 20)),
        axis.title.y = element_text(margin = margin(r = 20)),
        axis.text.y = element_text(size=rel(0.7)))
```

```{r}
fourth_join %>% 
  select(avg_stringency, avg_gresponse, avg_containtment, avg_econsupport, log_gdp, literacy_rate, h_sys_inf_index) %>% 
  pivot_longer(cols = everything(),
               names_to = "variable",
               values_to = "value") %>% 
  ggplot(aes(x=value))+
  geom_histogram(bins = 30, fill="navy blue")+
  facet_wrap(vars(variable),
             scales = "free")+
  theme_economist()+
  labs(x=" ")+
  theme(legend.title = element_text(size=rel (0.7), margin = margin(t = 20)),
        axis.text.x = element_text(size= rel(0.7)),
        axis.title.y = element_text(margin = margin(r = 20)),
        axis.text.y = element_text(size=rel(0.7)))

```

# Scatterplots for univariate relationships

```{r}
fourth_join %>% 
ggplot(aes(x=avg_ICT_index,y=edu_s))+
  geom_point()+
  geom_smooth(method=lm)+
  theme_economist()+
  labs(x= "ICT availability at schools",
       y= "Education Resiliance", 
       title= "Univariate Relationship Scatter Plot", 
       caption = "Graph by Cande Torres")+
  theme(axis.title.x = element_text(margin = margin(t = 20)),
        axis.title.y = element_text(margin = margin(r = 20)),
        axis.text.y = element_text(size=rel(0.7)),
        axis.text.x = element_text(size = rel(0.7),
        
        ))
                            
```

## Checking for Multicollinearity

```{r}
fourth_join %>% 
ggplot(aes(x=avg_ICT_index,y=gdp_per_capita))+
  geom_point()+
  geom_smooth(method = lm)+
  theme_economist()+
  labs(x= "ICT availability at schools",
       y= "GDP per capita", 
       title= "Univariate Relationship Scatter Plot", 
       caption = "Graph by Cande Torres")+
  theme(axis.title.x = element_text(margin = margin(t = 20)),
        axis.title.y = element_text(margin = margin(r = 20)),
        axis.text.y = element_text(size=rel(0.7)),
        axis.text.x = element_text(size = rel(0.7),
        
        ))
```

- There seems to be a correlation but not necesarilly a strong one.   

```{r}
fourth_join %>% 
ggplot(aes(x=avg_ICT_index,y=literacy_rate))+
  geom_point()+
  geom_smooth(method=lm)+
  theme_economist()+
  labs(x= "ICT availability at schools",
       y= "Literacy Rate", 
       title= "Univariate Relationship Scatter Plot", 
       caption = "Graph by Cande Torres")+
  theme(axis.title.x = element_text(margin = margin(t = 20)),
        axis.title.y = element_text(margin = margin(r = 20)),
        axis.text.y = element_text(size=rel(0.7)),
        axis.text.x = element_text(size = rel(0.7),
        
        ))
```

- Not necessarily correlated. 

# Thesis Analysis 

__MODEL 1__

Simple OLS.  

```{r}
model1<-lm(edu_s~ avg_ICT_index
   ,df4)
  summary(model1)
```
__MODEL 2__

Introduces impact of COVID-19.   

```{r}
model2<-lm(edu_s~ avg_ICT_index
           +avg_cases
           +avg_deaths
   ,df4) 
summary(model2)
```
__MODEL 3__

Introduces WDI controls.   

```{r}
model3<-lm(edu_s~ avg_ICT_index
           +avg_cases
           +avg_deaths
           +log_gdp
           +literacy_rate
           +h_sys_inf_index
   ,df4)
  summary(model3)
```
__MODEL 4__
Controls for different aspects of the Government Response to the Pandemic.   

```{r}
model4<-lm(edu_s~ avg_ICT_index
   +avg_cases
   +avg_deaths
   +log_gdp
   +literacy_rate
   +h_sys_inf_index
   +avg_stringency
   +avg_hp_index
   +avg_gresponse
   +avg_containtment
   +avg_econsupport
   ,df4) 
summary(model4)
```

__Check multicollinearity__

```{r}
vif(model4, df4)
```

```{r}
#create vector of VIF values
vif_values <- vif(model4)

#create horizontal bar chart to display each VIF value
barplot(vif_values, main = "VIF Values", horiz = TRUE, col = "steelblue")+
 scale_x_continuous(trans = scales::log_trans(),
                     breaks = scales::log_breaks())

#add vertical line at 5
abline(v = 5, lwd = 3, lty = 2)
```
Average economic support, average containtment and average government response are all showing massive values of multicollinearity. I will be dropping 2 of them


__MODEL 5__
Because GDP per capita seems to be correlated with ICT access at schools, we might want to drop the offender variable. 
```{r}
model5<-lm(edu_s~ avg_ICT_index
   #+avg_cases
   #+avg_deaths
   +log_gdp
   +literacy_rate
   +h_sys_inf_index
   +avg_stringency
   +avg_hp_index
   #+avg_gresponse
   #+avg_containtment
   #+avg_econsupport
   +sq_nCFR
   ,df4) 
summary(model5)
```


```{r}
vif(model5,df4)
```

- It is positive!!!! If you do not control for GDP per capita is positive!!!.  

__MODEL 6__

Robustness check introduces CFR instead of cases and deaths 

```{r}
model6<-lm(edu_s~ avg_ICT_index
   #+avg_cases
   #+avg_deaths
   +log_gdp
   +literacy_rate
   +h_sys_inf_index
   #+avg_stringency
   +avg_hp_index
   #+avg_gresponse
   +avg_containtment
   #+avg_econsupport
   +sq_nCFR
   ,df4) 
  summary(model6)
```
```{r}
vif(model6,df4)
```

__MODEL 7__

```{r}
model7<-lm(edu_s~ avg_ICT_index
   #+avg_cases
   #+avg_deaths
   #+log_gdp
   +literacy_rate
   +h_sys_inf_index
   +avg_stringency
   +avg_hp_index
   #+avg_gresponse
   #+avg_containtment
   #+avg_econsupport
    +sq_nCFR
   ,df4) 
  summary(model7)
```
```{r}
model8<-lm(edu_s~ avg_ICT_index
   +sq_nCFR
   +log_gdp
   +literacy_rate+h_sys_inf_index
   +avg_hp_index
   +avg_stringency
   #+avg_gresponse
   #+avg_containtment
   #+avg_econsupport
   ,df4) 
  summary(model8)
```

# Regional analysis 

```{r}
wide_4<- pivot_wider(fourth_join,
                      names_from = region_geo,
                      values_from = avg_ICT_index)
```


```{r}
wide_4 %>% 
  ggplot(aes(x=`Latin America & the Caribbean`,y= edu_s))+
  geom_point()+
  geom_smooth(method=lm)+
  theme_economist()+
  labs(x= "ICT availability at schools",
       y= "Education Resiliance", 
       title= "Scatter Plot for LATIN AMERICA", 
       caption = "Graph by Cande Torres")+
  theme(axis.title.x = element_text(margin = margin(t = 20)),
        axis.title.y = element_text(margin = margin(r = 20)),
        axis.text.y = element_text(size=rel(0.7)),
        axis.text.x = element_text(size = rel(0.7),
        
        ))
  
```

```{r fig.width=10}
fourth_join %>% 
  group_by(region_geo, country) %>% 
  mutate(ICT_region= mean(avg_ICT_index)) %>% 
  ggplot(aes(x=ICT_region, y=region_geo)) + 
  geom_col(fill="navy blue")+
  coord_flip()+
  theme_economist()+
  labs(x= "ICT availability at schools",
       y= "Regions", 
       title= "Regional Comparison on ICT access at schools", 
       caption = "Graph by Cande Torres")+
  theme(axis.title.x = element_text(margin = margin(t = 20)),
        axis.title.y = element_text(margin = margin(r = 20)),
        axis.text.y = element_text(size=rel(0.7)),
        axis.text.x = element_text(size = rel(0.7))
  )
```

- I believe the graphs is counting my observations as opposed to the actual ICT_level. 

```{r}
wide_4 %>% 
  select(`Latin America & the Caribbean`, country) %>%
  filter(country %in% c("Argentina", "Brazil", "Chile")) %>% 
  view()
```

- It seems that I was right.  

```{r}
df3<-fourth_join %>% 
  group_by(region_geo, avg_ICT_index, country) %>% 
  summarise() %>% 
  select(unique.x=country)
```

__Rename__

```{r}
df3 <-df3 %>% 
  transmute(country=unique.x)
```

```{r}
df3 <- df3 %>% 
  arrange(desc(avg_ICT_index)) %>% 
  mutate(label= round(avg_ICT_index, digits = 1))
```

```{r}
df3 %>% 
  filter(region_geo== "Latin America & the Caribbean") %>% 
  filter(country != "Dominican Republic") %>% 
  ggplot(aes(x=fct_reorder(country, avg_ICT_index, max), y=avg_ICT_index))+
  geom_col(fill= "navy blue")+
  labs( x="Countries",
        y= "ICT availability at schools",
        title="ICT index in Latin American Countries",
        caption="Graph by Cande Torres")+
  geom_text(aes(label = label), vjust = -0.5, position = "dodge" )+
  theme_economist()+
  theme(axis.title.x = element_text(margin = margin(t = 20)),
        axis.title.y = element_text(margin = margin(r = 20)),
        axis.text.y = element_text(size=rel(0.7)),
        axis.text.x = element_text(size=rel(0.7)),
        title = element_text(size=rel(0.8)))+
  expand_limits(y = 20)
```

```{r}
df3 %>% 
  filter(region_geo== "Latin America & the Caribbean") %>% 
#  filter(country != "Dominican Republic") %>% 
  ggplot(aes(x=fct_reorder(country, avg_ICT_index, max), y=avg_ICT_index))+
  geom_col(fill= "navy blue")+
  labs( x="Countries",
        y= "ICT availability at schools",
        title="ICT index in Latin American Countries",
        caption="Graph by Cande Torres")+
  geom_text(aes(label = label), vjust = -0.5, position = "dodge" )+
  theme_economist()+
  theme(axis.title.x = element_text(margin = margin(t = 20)),
        axis.title.y = element_text(margin = margin(r = 20)),
        axis.text.y = element_text(size=rel(0.7)),
        axis.text.x = element_text(size=rel(0.7)),
        title = element_text(size=rel(0.8)))+
  expand_limits(y = 20)
```

```{r}
df5<-fourth_join %>% 
  group_by(region_geo, avg_ICT_index, edu_s, country) %>% 
  summarise() %>% 
  select(unique.x=country)
```

__Rename__

```{r}
df5 <-df5 %>% 
  transmute(country=unique.x)
```

```{r}
df5 <- df5 %>% 
  arrange(desc(edu_s)) %>% 
  mutate(label= round(avg_ICT_index, digits = 4))
```

```{r}
df5 %>% 
  filter(region_geo== "Latin America & the Caribbean") 
  
```

#Regional Average ICT index
```{r}
df5 %>% 
  group_by(region_geo) %>% 
  summarise(avg_ict= mean(avg_ICT_index))
```
# Order countries by ICT index

```{r}
df4 %>% 
  group_by(country) %>% 
  summarise(avg_ICT_index) %>% 
  arrange(desc(avg_ICT_index))
```

------------------------------


# Creating a table to display all the models

```{r}
library(texreg)
screenreg(list(model1, model2, model3, model4, model5, model6, model7), 
          custom.coef.names = c("Intercept",
                                "ICT in schools Index", 
                                "COVID-19 Cases",
                                "COVID-19 Deaths",
                                "Log GDP per capita", 
                                "Literacy Rate",
                                "Strengh of Health System Index",
                                "Government Stringency Index",
                                "Health Policy Index (2020)",
                                "Government Response to the Pandemic Index",
                                "Containtment of the virus Index",
                                "Government Economic Support",
                                "Critical Fatality Ratio (squared)"),
          stars = c(0.01, 0.05, 0.1),
          custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)", "(6)", "(7)"),
          digits = 3 #change decimal places
)
```




__Making it nice for LateX__


```{r}
library(texreg)
texreg(list(model1, model2, model3, model4, model5, model6, model7), 
          custom.coef.names = c("Intercept",
                                "ICT in schools Index", 
                                "COVID-19 Cases",
                                "COVID-19 Deaths",
                                "Log GDP per capita", 
                                "Literacy Rate",
                                "Strengh of Health System Index",
                                "Government Stringency Index",
                                "Health Policy Index (2020)",
                                "Government Response to the Pandemic Index",
                                "Containtment of the virus Index",
                                "Government Economic Support",
                                "Critical Fatality Ratio (squared)"),
          stars = c(0.01, 0.05, 0.1),
          custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)", "(6)", "(7)"),
          digits = 3 #change decimal places
)
```





